### 2024-08-12 doc/Thesis/chapter/020-theory-materials.tex
leybold and spectrometer info added

\todo{what were the used settings: leybold etc.}
%Prior to \gls{iv} measurements the samples were sputtered with aluminium through a mask to produce a multitude of equidistant contacts with a Leybold UNIVEX450C Sputter System.
%Directional current sputtering was used with argon as inert gas at \SI{0.005}{\milli\bar} and with a power of \SI{40}{\watt} for \SI{700}{\second}.

@@

%\td{Frank-Condon rules, spin verbot and symmetrie verbot are ausschlaggebend für the resulting spectrum. }
%differences to \gls{uv}\gls{vis}: transmission instead of absorbance, higher energy left instead right in plot, base line on top instead of bottom.
\td{specifications of instruments}

>>>>

%\todo{what were the used settings: leybold etc.}
%\todo{40W, t=700s, p=0.002 mbar, gas inlet= 6 sccm (Ar), no heating or cooling
%sccm = Standard cubic centimetres per minute}
The settings on the Leybold sputtering system were as follows: 40 W for 700 seconds at 0.002 mbar and a argon gas inlet of 6 sccm (standard cubic centimeters per minute). % with a pressure of 0.002 mbar. 
%Prior to \gls{iv} measurements the samples were sputtered with aluminium through a mask to produce a multitude of equidistant contacts with a Leybold UNIVEX450C Sputter System.
%Directional current sputtering was used with argon as inert gas at \SI{0.005}{\milli\bar} and with a power of \SI{40}{\watt} for \SI{700}{\second}.

@@

%\td{Frank-Condon rules, spin verbot and symmetrie verbot are ausschlaggebend für the resulting spectrum. }
%differences to \gls{uv}\gls{vis}: transmission instead of absorbance, higher energy left instead right in plot, base line on top instead of bottom.
%\td{specifications of instruments}
Reflectance and transmittance were measured at \ang{0} and \ang{20} incident angle, respectively, with a Bruker Vertex 70.
